{\boldmath Pseudoscalar top-Higgs coupling: Exploration of $\mathrm{CP}$-odd observables to resolve the sign ambiguity }

### 2016-03-02 Paper_ttbarH_Draft.tex
KK edits to Sec. IIIB

same in both cases, but with
opposite sign for $\kp=\kpt=1$ and $\kp=-\kpt=1$, thus allowing

@@

in both cases.  In order to quantify the mentioned shifts, we have fitted
the simulated distributions with the following function proposed in
\cite{Ellis},

@@

To the extent that this equation is exact we note that
Eq.~(\ref{eq29}) gives $\mathcal{A}(\epsilon_i)=4a_1 \sin\delta$. With
this fitting function, we obtain phase shifts approximately between

@@

not good enough, being worse in the case of the $\epsilon_1$
distributions for which $\chi^2/\mathrm{d.o.f}$ is in the range
$1.69$-$3.86$, in contrast to the range $0.53$-$1.16$ obtained for
$\epsilon_2$. The main impact on the deviation from the functional
form proposed in Eq.~(\ref{eq27}) appears to be caused by the $\Delta
R_{ll}$ cut we have imposed. In fact, when this cut is turned off the
above ranges for $\chi^2/\mathrm{d.o.f}$ modify to $0.75$-$1.14$ and
$0.44$-$1.07$ for the $\epsilon_1$ and $\epsilon_2$ distributions
respectively. In Tables \ref{table3} and \ref{table4} we list the

@@

relaxed. The results for the TP $\epsilon_3$ are pretty similar to
those for $\epsilon_2$ but with opposite sign in the phase shifts of
the $\mathrm{CP}$-mixed hypotheses and hence we do not include them
here. In addition, we show in Fig.~\ref{fig7} the angular
distributions along with the fit curves for both $\mathrm{CP}$-mixed
cases when no cut is imposed in $\Delta R_{\ell\ell}$.

@@

  d\Delta\phi_1(n_t,n_{\tbar}))$ related to the TP
  $\epsilon_1=\epsilon(t,\tbar,n_t,n_{\tbar})$ when the $\Delta
  R_{\ell\ell}$ is turned off. Note that the parameter $a_1$ change
  its sign for $\kp=0,\kp=1$.}

@@

  d\Delta\phi_2(n_t,n_{\tbar}))$ related to the TP
  $\epsilon_2=\epsilon(Q,\tbar,n_t,n_{\tbar})$ when the $\Delta
  R_{\ell\ell}$ is turned off. Note that the parameter $a_1$ change
  its sign for $\kp=0,\kp=1$.}

@@

  $\epsilon_1=\TPa$ and $\epsilon_2=\TPb$ respectively for the

@@

  (right) when the $\Delta R_{\ell\ell}$ cut is turned off. Also, the
  corresponding fit curves are displayed in red.}

>>>>

same in both cases, but is in the
opposite direction for $\kp=\kpt=1$ compared to $\kp=-\kpt=1$, thus allowing

@@

in both cases.

In order to quantify the shifts discussed above, we have fitted
the simulated distributions with the following function, which was proposed in
Ref.~\cite{Ellis},

@@

To the extent that the above expression is exact, we note that
Eq.~(\ref{eq26}) {\bf (KK: corrected the equation number; please check\ldots )}
gives $\mathcal{A}(\epsilon_i)=4a_1 \sin\delta$. With
this fitting function, we obtain phase shifts $\delta$ that
are approximately between

@@

not very good, particularly for $\epsilon_1$.  The
$\chi^2/\mathrm{d.o.f}$ for the fits in this case are in the range
$1.69$-$3.86$, while for $\epsilon_2$ they are in the range $0.53$-$1.16$.
{\bf (KK: Did we do 4 fits for each $\epsilon$?  Or only 2?  If only 2, maybe
  saying ``in the range'' is not quite correct, since the two
  data points are simply the endpoints of the ``range''.  If
  the range includes all 4 fits for each, maybe we could state that
  explicitly, since the preceding sentences are only discussing the two
  mixed-CP scenarios.)}
The leading source of the deviation from the functional
form proposed in Eq.~(\ref{eq27}) appears to be the $\Delta
R_{ll}$ cut that we have imposed. In fact, when this cut is turned off, the
above ranges for $\chi^2/\mathrm{d.o.f}$ become $0.75$-$1.14$ and
$0.44$-$1.07$ for the $\epsilon_1$ and $\epsilon_2$ distributions,
respectively. Tables \ref{table3} and \ref{table4} list the

@@

relaxed.  Also, 
Fig.~\ref{fig7} shows the angular
distributions, along with the fit curves, for the $\mathrm{CP}$-mixed
cases with the $\Delta R_{\ell\ell}$ cut turned off.
The results for the TP $\epsilon_3$ are relatively similar to
those for $\epsilon_2$, except that the phase shifts have the opposite
sign in the $\mathrm{CP}$-mixed cases.  Given this similarity
we do not include the results for the $\epsilon_3$ distribution
here. 

@@

  d\Delta\phi_1(n_t,n_{\tbar}))$ (related to the TP
  $\epsilon_1=\epsilon(t,\tbar,n_t,n_{\tbar})$) with the $\Delta
  R_{\ell\ell}$ cut turned off. Note that the sign of the parameter $a_1$
  changes for $\kp=0,\kp=1$, compared to the
  other cases.  {\bf (KK: Do we restrict $\delta$ to be between
    $\pm \pi/2$?  If not, we could require $a_1$ to always
    be positive, and absorb the sign change by a shift of $\delta$ by $\pi$
    or ssomething.  Maybe we should clarify the range allowed for $\delta$.)} }

@@

  d\Delta\phi_2(n_t,n_{\tbar}))$ (related to the TP
  $\epsilon_2=\epsilon(Q,\tbar,n_t,n_{\tbar})$), with the $\Delta
  R_{\ell\ell}$ cut turned off. As was the case in Table~\ref{table3},
  the sign of the parameter $a_1$ changes for
  $\kp=0,\kp=1$.}

@@

  $\epsilon_1=\TPa$ and $\epsilon_2=\TPb$, respectively, for the

@@

  (right).  The $\Delta R_{\ell\ell}$ cut was turned off when
  generating these results. The
  corresponding fit curves [see Eq.~(\ref{eq27})] are displayed in red.}
